%% A concise summary that highlights your key qualifications and how they align
%% with the employer’s needs. Mention your experience with relevant technologies
%% and your enthusiasm for contributing to their team.

%% Patricia: XX years development experience. Born in CZ, lived in Barcelona,
%% London, and now happily settled and married in Mexico. Sabbatical of xx months
%% taken for self development, to explore South America, and to walk the complete
%% Camino (from Paris to Santiago).
\section{Professional Summary}

Seasoned software developer with over 15 years of experience in Ruby, JavaScript, and early adoption of frameworks like Angular.js and React.js. Recently transitioned to Clojure, drawn by its stable ecosystem and smart community. Proven ability to deliver reliable, high-quality software solutions.

After a sabbatical to recover from burnout and refocus my career goals, I delved deeply into stress management, meditation, and breathwork. This period of self-improvement provided me with an in-depth understanding of how to manage and retain the flow state, safeguarding against burnout. I also studied Traditional Chinese Medicine (TCM) and Ayurveda to improve my diet and overall health. During this time, I discovered Clojure, which reignited my passion for software development.

Eager to leverage my refreshed perspective and new skills to contribute to a forward-thinking company like LoanPro, where I can make a meaningful impact.

%% List skills that are directly relevant to the position. Include both technical
%% and soft skills. Ensure these align with the job description and the employer’s
%% needs.

%% Languages & Frameworks: Ruby, JavaScript, Angular.js, React.js, Clojure
%% Development Tools: Git, Docker, Jenkins, RabbitMQ
%% Methodologies: Agile, TDD, Continuous Integration
%% Soft Skills: Problem-solving, adaptability, effective communication, teamwork
\section{Key Expertise}

\startitemize[joinedup,columns,two]
  \item Clojure, ClojureScript & Babashka.
  \item Agile, SCRUM, Kanban.
  \item Unit testing, TDD & integration testing.
  \item Git
  \item CI & CD, Jenkins
  \item AMQP, RabbitMQ
  \item DigitalOcean & AWS.
  \item JavaScript & React.js.
  \item Work in healthcare & HIPAA compliance. %% Banking is a similar sector in terms of security! Highlight that.
    %% Financial planning. -> PATRICIA!!!
  \item Linux, ZSH/Bash, Vim & Emacs.
  \item Containerization using Docker.
  \item Advanced stress management techniques, safe-guarding against burn-out.
  \item Secret {\em flow state} management techniques of Tibetan Buddhism.
\stopitemize

%\vskip -15mm

\section{Professional Experience}

\define[3]\Position{
  \blank
  \setupframed[height=1cm,frame=off,offset=0pt]
  \startcombination[2]
    {\framed[width=12.5cm,top=\vss,bottom=\vss,align=right]{%
    {\bfa #1}\\
    {\sc #2}
    }}{}
    {\framed[width=7cm,align=flushright,top=\vss,bottom=\vss]{%
    {\bf #3}
    }}{}
  \stopcombination
}

%% I was 18 when I started working there.
\useURL[root-profile][https://www.root.cz/autori/jakub-stastny]
\Position{Root.cz}{Technical redactor\endnote{My articles for Root.cz: \from[root-profile]}}{December 2006~-- August 2008}
\startitemize
  \item Worked as a technical redactor on the second largest Linux site in the Czech Republic at the time.
  \item Wrote news items and in-depth articles daily, contributing to the site's growth and relevance.
  \item Developed comprehensive knowledge of Linux ecosystems and community dynamics.
  \item Regularly participated in Linux conferences and meetups, expanding professional network.
  \item Contributed to the growth of Linux awareness and adoption in the Czech Republic.
\stopitemize

\Position{OSS work & contracting}{Junior software developer}{August 2008~--May 2009}
\startitemize
  %% - Git hooks deployment, pupu -> bower.
  %% - Deep commitment to OSS, Rango with template inheritance. rSpec contribution, what else. GitHub since 2008.
  %% SproutCore (2007): A framework designed to help developers build robust desktop-like applications in the browser. It inspired many concepts that were later used in Ember.js.
  \item While I loved Linux, I knew programming was my true passion. Already in my time at Root.cz I was writing a lot about programming, but it was time to take my passion next level.
  \item Was attending PRUG meetups from the first, gave talks, Ostrava on Rails.
  \item Few sporadic contracts with Ruby on Rails and JS (editing images).
\stopitemize

%% I was 20 yo when I moved to London.
\useURL[jgp][https://www.jobsgopublic.com]
\Position{JobsGoPublic.co.uk}{Junior Ruby & JavaScript developer}{May 2009~--April 2010}
\startitemize
  \item Czech Republic wasn't the place to do Ruby, so I set myself for London.
  \item The key learning here was working with legacy systems.
  \item Despite being supposedly junior, I ended up teaching the other developers as they transitioned from ColdFusion.
\stopitemize

\useURL[dachis-acquisition][https://www.venturecapitaljournal.com/dachis-group-buys-headshift]
\Position{Headshift Ltd}{Junior Ruby & JavaScript developer}{April 2010~--June 2011}
{\em Headshift Ltd was acquired by the Dachis group\endnote{\from[dachis-acquisition]}.}

\startitemize
  \item IE6 as I was the best in JS.
  \item Agency work, we were expected to pick up shit fast.
  \item ...
\stopitemize

%% Key Contributions: Highlight specific achievements and how they benefited
%% the company (e.g., improved performance, enhanced stability).
%% Technologies Used: Mention technologies relevant to the job you’re applying for.
\useURL[ruby-amqp][https://github.com/ruby-amqp]
\Position{VMware, RabbitMQ team}{Independent Ruby contractor}{07/2021~-- July 2021}
{\em RabbitMQ is now part of SpringSource.}

\startitemize
  \item Ruby AMQP \endnote{\from[ruby-amqp]}. Redesigned from scratch with great performance.
  \item Dublin, Poland, conference talks. Articles?
  \item ...
\stopitemize

\Position{Start-ups}{Various roles}{07/2021~-- July 2021}
\startitemize
  \item {\bf HowAreYou:} a UK-based healthcare start-up.
  \item {\bf YNiche:} conferencing via...
  \item {\bf PayPerTask:} My own try.
\stopitemize

%% Key Contributions: Focus on successful projects and outcomes that showcase
%% your ability to deliver results.
%% Client Impact: Describe how your work positively impacted clients.
\Position{TopTal -- Remote}{Senior Ruby & JavaScript developer}{07/2021~-- July 2021}
\startitemize
  \item Agency work for one of the top agencies in the world.
  \item Coordination across multiple time-zones and cultures.
\stopitemize

\Position{Sabatical}{}{March 2021 -- July 2024}
\vskip -5mm
I’ve seen the rapid changes in the IT industry and the burnout that often follows. I nearly became one of those burnt-out developers. But I learned to focus on the bigger picture: creating lasting value. I deliver high-quality work on time, value team collaboration, and always keep the end-user in mind. My commitment to customer satisfaction is unwavering, ensuring that every project meets and exceeds expectations.

I reflected and realised I was foolish all along: it wasn't about the fancy new library, it was about the customer.

Found Clojure, love reignited.

\startitemize[before={}, after={}]
  \item Took a break due to burnout and the desire to move away from work in agencies and early-stage startups.
  \item Delved deeply into stress management, meditation, and breathwork.
  \item Gained an in-depth understanding of how these techniques can be used to manage and retain the flow state.
  \item Learned how to use stress management techniques as a safeguard against burnout.
  \item Studied Traditional Chinese Medicine and Ayurveda to improve diet and overall health.
  \item The free time allowed me to discover and learn Clojure, which reignited my passion for software development.
  \item Camino de Santiago de Compostela from France all the way to the Atlatic ocean in Galicia, Spain.
\stopitemize

\Position{BizMentor Ltd}{Senior Clojure & ClojureScript developer}{07/2021~-- July 2021}
\startitemize
  \item A
  \item B
  \item ...
\stopitemize

\blank \section{Personal Projects}
I love OSS and have a great commitment to it. I spent endless hours programming and learning and I still do, perhaps more than ever, now since I discovered Clojure. Thanks to that, I have 114 OSS repositoris on \goto{@botanicus}[url(https://github.com/botanicus)] and another 56 on \goto{@jakub-stastny}[url(https://github.com/jakub-stastny)].

\Position{Rango}{\from[rango]}{2014 -- present}
\startitemize
  \item Rango was Django-style Ruby framework with template inheritance.
  \item Mostly personal, but Rango got \goto{some traction}[url(http://www.rubyinside.com/rango-ruby-web-app-framework-2858.html)].
  \item I gave a talk about Rango at Ruby Manor 2009\endnote{Rango Ruby Manor 2009 slides \from[ruby-manor]}.
\stopitemize

\Position{Pupu}{\from[pupu]}{2014 -- present}
\startitemize
  \item Pupu was Bower-like static asset installed, but 10 years before Bower came about.
\stopitemize

\Position{Docker Project Manager}{\from[dpm]}{2014 -- present}
\startitemize
  \item Since I was working in agency settings, being able to set up project in sandbox environment was key.
  \item Generate SSH keys, then persist them across builds, persist ZSH history, ENV.
  \item Written in Crystal, multi-stage Docker image, small.
\stopitemize

\Position{Emacs Tasks}{\from[et]}{2023 -- present}
\startitemize
  \item Written in Clojure, Babashka-compatible.
  \item A
  \item B
\stopitemize

\section{Education}
\startitemize
  \item {\bf Gymnázium Prachatice}\hfill{September 2000 -- June 2007}
  \startitemize
    \item Prestige grammar school with an eight-year program.
    \item I ranked second in the entrance examination.
    \item Since I was working from my penultimate year and IT was my passion, I eventually dropped out.
  \stopitemize
\stopitemize

\vfill
\section{Footnotes}
\placenotes[endnote][criterium=all] % Places all footnotes here
