%% Patricia: XX years development experience. Born in CZ, lived in Barcelona,
%% London, and now happily settled and married in Mexico. Sabbatical of xx months
%% taken for self development, to explore South America, and to walk the complete
%% Camino (from Paris to Santiago).

%% A concise summary that highlights your key qualifications and how they align
%% with the employer’s needs. Mention your experience with relevant technologies
%% and your enthusiasm for contributing to their team.
\section{Professional Summary}
Software Engineer with 15 years of experience in developing scalable, robust software solutions. Skilled in Clojure, Ruby on Rails, and JavaScript. Proven track record in building and maintaining complex systems with backward compatibility. Experienced in collaborating with cross-functional teams to deliver high-quality, customer-centric solutions. Seeking to contribute to LoanPro’s mission of delivering advanced financial software.

\section{Key Expertise}
\startitemize[joinedup,columns,two]
  \item API development & 3rd party integration.
  \item Clojure & functional programming.
  \item JavaScript, ClojureScript, React.js & Reagent.
  \item DigitalOcean & AWS.
  %% \item Version control with Git.
  \item Software testing, CI & CD pipelines, Jenkins.
  \item Agile development, SCRUM, Kanban & XP.
\stopitemize

\section{Professional Experience}
\Position{BizMentor}{Clojure & ClojureScript developer}{Feb 2023~-- Feb 2024}
\vskip -0.4em
\startitemize
  \item Developed AI-driven growth projection app using Reagent for the web and Clojure for backend.
  \item Implemented advanced AI prediction algorithms for startup growth based on industry data.
  \item Created robust calculation and AI engine to ensure accurate projections and performance.
\stopitemize

\Position{Sabbatical}{}{}
\vskip -1.7em
During the pandemic, I experienced burnout and took a sabbatical to recharge. During this time, I discovered Clojure, which reignited my passion for programming. My long-standing preference for functional programming, combined with Clojure’s backward compatibility, focus on pure functions, and the possibilities offered by Lisp such as macros and structural editing, renewed my interest in software development.

%% Key Contributions: Focus on successful projects and outcomes that showcase
%% your ability to deliver results.
%% Client Impact: Describe how your work positively impacted clients.
\Position{TopTal -- Remote}{Ruby & JavaScript developer}{Jul 2015~-- May 2021}
\vskip -0.4em
\startitemize
  \item Selected by TopTal, the top 3\% of developers globally, for numerous client projects.
  \item Collaborated across teams, time zones, and cultures to deliver high-quality solutions.
  \item Quickly mastered new programming and soft skills, demonstrating adaptability and rapid learning.
\stopitemize

%% Key Contributions: Highlight specific achievements and how they benefited
%% the company (e.g., improved performance, enhanced stability).
%% Technologies Used: Mention technologies relevant to the job you’re applying for.
\useURL[ruby-amqp][https://github.com/ruby-amqp]
\Position{VMware, RabbitMQ team}{Independent Ruby contractor}{Apr 2010~-- Jan 2012}
\vskip -0.4em
%% {\em RabbitMQ is now part of SpringSource.}

\startitemize
  \item Redesigned and rewrote Ruby AMQP library for improved performance and reliability.
  \item Enhanced library design, resulting in cleaner code and significantly fewer bugs.
  \item Delivered talks on AMQP & RabbitMQ at various meetups and local conferences.
\stopitemize

\section{Personal Projects}
I love OSS and have a great commitment to it.
I have 114 repositoris on \goto{@botanicus}[url(https://github.com/botanicus)] and 56 on \goto{@jakub-stastny}[url(https://github.com/jakub-stastny)].

\useURL[pupu][https://github.com/botanicus/pupu][][Pupu]
\useURL[rango][https://github.com/botanicus/rango][][Rrango]
\useURL[dpm][https://github.com/jakub-stastny/docker-project-manager][][Docker Project Manager]
\useURL[et][https://github.com/jakub-stastny/et][][Emacs Tasks]
\useURL[ruby-manor][http://www.slideshare.net/botanicus/rango]

\startitemize
  %% \item Rango was Django-style Ruby framework with template inheritance.
  %% \item Mostly personal, but Rango got \goto{some traction}[url(http://www.rubyinside.com/rango-ruby-web-app-framework-2858.html)].
  %% \item I gave a talk about Rango at Ruby Manor 2009\endnote{Rango Ruby Manor 2009 slides \from[ruby-manor]}.

  \item \from[pupu] was Bower-like static asset installed, but 10 years before Bower came about.

  %% \item Since I was working in agency settings, being able to set up project in sandbox environment was key.
  %% \item Generate SSH keys, then persist them across builds, persist ZSH history, ENV.
  %% \item Written in Crystal, multi-stage Docker image, small.
  \item \from[dpm] was a multi-stage Docker image managing the lifecycle of multiple projects, serving as a Docker-powered sandbox for agency work.
  \item \from[et]\high{\color[red]{WIP}} is a build tool with tasks defined using literate programming, similar to Make.
\stopitemize
